%!TEX TS-program = xelatex
\documentclass[]{src/friggeri-cv}
\usepackage{afterpage}
\usepackage{hyperref}
\usepackage{color}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{progressbar}
\usepackage{changepage}

% Remove link decorations: https://tex.stackexchange.com/questions/823/remove-ugly-borders-around-clickable-cross-references-and-hyperlinks
\hypersetup{
    pdftitle={Brian Paul Beatty},
    pdfauthor={Brian Beatty},
    pdfsubject={Brian Beatty - Resume},
    pdfkeywords={aws,bpmn,c++,c,camunda,developer,devops,docker,git,java,jenkins,kafka,linux,os,podman,programming,python,resume,software,sysadmin,ublue},
    pdfborder=0 0 0,
    colorlinks=false,
    allbordercolors=white
}

\definecolor{pblue}{HTML}{0395DE}

\begin{document}
\header{Brian}{ P. Beatty}
    {}

% Fake text block acting as a visual top divider separator
\fcolorbox{white}{gray}{\parbox{\dimexpr\textwidth-2\fboxsep-2\fboxrule}{%
.....
}}

% In the aside, each new line forces a line break
\begin{aside}
  \section{Location}
    Papillion, NE, USA
    ~
  \section{Mail}
    \href{mailto:brian@27megahertz.com}{\textbf{brian@}27megahertz.com}
    ~
  \section{Source}
    \href{https://github.com/bpbeatty/resume}{\textbf{github.com/bpbeatty/resume}} \quad
    \textit{\small (Built via CI/CD Pipeline)}
    ~
  \section{Languages}
    \begin{tabular}{p{1.1cm} p{2.5cm}}
      \progressbar[width=1.1cm,filledcolor=green]{1.0} & {BASH} \\
      \progressbar[width=1.1cm,filledcolor=green]{0.85} & {Python} \\
      \progressbar[width=1.1cm,filledcolor=green]{0.9} & {Java} \\
      \progressbar[width=1.1cm,filledcolor=green]{0.75} & {C/C++} \\
      \progressbar[width=1.1cm,filledcolor=green]{0.7} & {MATLAB} \\
      \progressbar[width=1.1cm,filledcolor=green]{0.7} & {FORTRAN}
    \end{tabular}
    ~
  \section{Personal Skills}
    \begin{tabular}{p{1.2cm} p{2.0cm}}
      \progressbar[width=1.1cm,filledcolor=blue]{1.0} & {Ownership} \\
      \progressbar[width=1.1cm,filledcolor=blue]{1.0} & {Collaboration} \\
      \progressbar[width=1.1cm,filledcolor=blue]{1.0} & {Organization}
    \end{tabular}
    ~
  \section{Projects}
    \item[\rightarrow]\href{https://github.com/bpbeatty/bos}{\textbf{bos:} Personal OS Build}
    \item[\rightarrow]\href{https://www.northropgrumman.com/space/chasing-the-ionosphere}{\textbf{Chasing Ionosphere}}
    \item[\rightarrow]\href{https://github.com/bpbeatty/fedora-coreos-proxmox}{\textbf{fedora-coreos-proxmox}}
    ~
  \section{Technologies}
    \item[\rightarrow]{Ansible}
    \item[\rightarrow]{Docker/Podman}
    \item[\rightarrow]{GNURadio}
    \item[\rightarrow]{libvirt/qemu/kvm}
    \item[\rightarrow]{Linux}
    ~
\end{aside}

\section{Education}
\begin{entrylist}
  \entry
    {2014}
    {Bachelors of Science: Electronics Engineering}
    {University of Nebraska--Lincoln}
    {Strong focus on systems architecture, digital design, and hands-on laboratory application.}
\end{entrylist}

\section{Experience}
\begin{entrylist}
  \entry
    {Jan 2026 - Present}
    {Sentinel}
    {Northrop Grumman}
    {\begin{itemize}
        \item Spearheading the establishment of modern development and engineering standards.
        \item Driving security compliance initiatives and systematic technical debt remediation.
        \item Optimizing infrastructure architectures and centralized code repositories for efficiency.
        \item Providing targeted mentorship to junior team members to build core technical skillsets.
    \end{itemize}}
  \entry
    {Dec 2021 - Dec 2025}
    {Deep-Space Advanced Radar Capability}
    {Northrop Grumman}
    {\begin{itemize}
        \item Implemented robust, microservice-based system architectures utilizing the Java Spring Boot framework.
        \item Conducted detailed code reviews and delivered constructive feedback to maximize velocity.
        \item Mentored junior engineers and created tailored onboarding paths to accelerate ramp-up times.
        \item Ported complex mathematical algorithms from MATLAB to resilient Java for production systems.
    \end{itemize}}
  \entry
    {2021 - 2023}
    {Edge Of Space}
    {Northrop Grumman}
    {\begin{itemize}
        \item Designed and implemented reliable protocols for precision launch and recovery operations.
        \item Successfully launched high-altitude balloon payloads to support radio signal geolocation.
        \item Served as Lead Software Developer, customizing open-source software to interface smoothly with COTS components for balloon beacons.
        \item Developed a ground-based Software Defined Radio (SDR) system for real-time geolocation.
        \item Utilized MATLAB for extensive post-processing analysis of raw IQ signal data.
    \end{itemize}}
\end{entrylist}

%% Force clean break to Page 2 %%
\clearpage

%% Start Page 2 with full left-to-right layout alignment %%
\begin{adjustwidth}{-4.8cm}{0cm} 
\begin{entrylist}
  \entry
    {Jan 2021 - Dec 2021}
    {Protected Forward Comms HF}
    {Northrop Grumman}
    {\begin{itemize}
        \item Designed and built a 30W Software Defined Radio capable of multiple Over-The-Air waveforms (FM, SSB, BPSK).
        \item Performed scientific ionospheric studies to characterize link reciprocity in HF NVIS communication systems for DARPA.
        \item Obtained Amateur Extra Class radio operator license in support of ongoing project requirements.
    \end{itemize}}
  \entry
    {Jan 2021 - Dec 2021}
    {Sagittarius Ground}
    {Northrop Grumman}
    {\begin{itemize}
        \item Built software capabilities leveraging Air Force weather models to assist mission planning for ground-to-satellite arrays.
        \item Designed and developed a REST service calculating decibel loss for links utilizing ITU models and forecast weather data.
    \end{itemize}}
  \entry
    {Mar 2019 - Sep 2020}
    {AFWWEBS Project, SEMS III}
    {Northrop Grumman}
    {\begin{itemize}
        \item Lead technical contributor for the AFWWEBS Di2E CI/CD Pipeline from initial concept, design, implementation, to validation.
        \item The project took a single AFWWEBS repository, Weatherview, and implemented a CI/CD pipeline, from developer commit to artifact storage.
        \item Enabled moving 30+ repositories from on prem hardware to Amazon gov cloud. Enabled developers to work remotely and deploy software on Air Force systems.
        \item Lead technical contributor for the Skymap visualization project from initial concept, design, implementation, to validation.Lead technical contributor for the Skymap visualization project from initial concept, design, implementation, to validation.
        \item The project took data received from SWAFS and visualized the data in a web browser.
    \end{itemize}}
  \entry
    {Oct 2016 - Mar 2019}
    {SWAFS Project, SEMS III}
    {Northrop Grumman}
    {\begin{itemize}
        \item Served as Lead Technical Contributor for the Skymap project from concept design through validation phases.
        \item Integrated academic-level software packages (SKYMAP) seamlessly with existing enterprise SWAFS capabilities (SNFT).
    \end{itemize}}
\end{entrylist}
\end{adjustwidth}

\end{document}
